---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---



```{r}
medcon <- read.csv("MED_Conts_Toxins_teliko_2.csv")
medcon

medcon <- medcon[-c(192,271,273, 431,836), ]
medcon

```

```{r}
library(tidyr)
library(dplyr)
library(stringr)

```

```{r dpi=72, fig.width=4, fig.height=4}
test <- medcon %>%
  select(Species, Cyanotoxin) %>%
  filter(str_detect(Species, "Microcystis")) %>% 
  mutate(yesno = 1) %>%
  distinct %>%
  spread(Species, yesno, fill = 0)

heatmap(t(as.matrix(test[,-1])))
```


```{r}
summary(medcon)
```

## Find the unique Species in the Mediterranean basin

```{r}
medcon %>% 
  filter(Continent == "Mediterranean") %>% 
  group_by(Species) %>% 
  distinct(Species)
```


## Table with grouped Species and Cyanotoxins for each taxon in Mediterranean

```{r}
species_cyanotox <- medcon %>%
  filter(Continent == "Mediterranean")%>%
  group_by(Species, Cyanotoxin) %>%
  summarize(Number_of_records = n()) %>%
  select(Species,  Cyanotoxin)
species_cyanotox
```

```{r}
species_cyanotox_cont <- medcon %>%
  filter(Continent != "Mediterranean")%>%
  group_by(Species, Cyanotoxin) %>%
  summarize(Number_of_records = n()) %>%
  select(Species, Cyanotoxin )
species_cyanotox_cont
```

##Οι κύριοι παραγωγοί τοξινών στη Μεσόγειο (συνολικά 9) + γράφημα

```{r}
main_toxin_producers_MED <- medcon %>%
  filter(Continent == "Mediterranean")%>%
  group_by(Species)%>%
  summarize(Number_of_records = n())%>%
  arrange(desc(Number_of_records))

head(main_toxin_producers_MED, 9)
library(ggplot2)

main_toxin_producers_cont <- 
  ggplot(head(main_toxin_producers_MED,9), 
         aes(x = reorder(Species, -Number_of_records), 
             y = Number_of_records, fill = Species)) + 
  geom_bar(stat = "identity") + 
  theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.title = element_text(size = 14), 
    axis.text.x = element_text(size = 12, 
        vjust = 0.5, angle = 75), plot.title = element_text(size = 15), 
    panel.background = element_rect(fill = NA), 
    legend.background = element_rect(fill = NA, 
        size = 0.1)) +
  labs(x = "Species", size = 14) + 
  theme(legend.position = "none") + 
  coord_flip()  + 
  theme(axis.text.x = element_text(angle = 0))+ 
  geom_text(aes(label=Number_of_records), hjust=3, color="black", size=4) + 
  theme(axis.title = element_text(size = 16), 
    axis.text = element_text(size = 12), 
    plot.title = element_text(size = 14), 
    plot.background = element_rect(colour = NA)) +
  labs(y = "Number of records") + 
  theme(panel.grid.major = element_line(colour = NA), 
    panel.grid.minor = element_line(colour = NA), 
    panel.background = element_rect(linetype = "solid"), 
    plot.background = element_rect(linetype = "solid")) + 
  theme(axis.ticks = element_line(colour = "black"), 
    axis.text = element_text(size = 20, colour = "black"), 
    axis.text.x = element_text(size = 14, 
        colour = "black"), axis.text.y = element_text(size = 14, 
        colour = "black"))

main_toxin_producers_cont + theme(
  panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA)
        )

ggsave("main_toxin_producers_MED.png", bg = "transparent")
  
```

## Number of cyanotoxins per species

```{r}
cyanotoxin_per_species <- medcon %>%
  filter(Continent == "Mediterranean")%>%
  select(Species, Country, Cyanotoxin)%>%
  group_by(Species, Cyanotoxin)%>%
  summarize(N_toxin = n())%>%
  arrange(Species, Cyanotoxin)
cyanotoxin_per_species

```

## Cyanotoxins per Species in the World except Mediterranean

```{r}
cyanotoxin_per_species <- medcon %>%
  filter(Continent != "Mediterranean")%>%
  select(Species, Country, Cyanotoxin)%>%
  group_by(Species, Cyanotoxin)%>%
  summarize(N_toxin = n())%>%
  filter(N_toxin >1) %>% 
  arrange(Species, Cyanotoxin)
cyanotoxin_per_species
```

## Main toxin producers in the other Continents, not Mediterranean

```{r}
main_toxin_producers_globally <- medcon %>%
  filter(Continent != "Mediterranean") %>% 
  group_by(Species)%>%
  summarize(Number_of_records = n())%>%
  arrange(desc(Number_of_records))
main_toxin_producers_globally

main_toxin_producers_cont <- ggplot(head(main_toxin_producers_globally,9), 
                                  aes(x = reorder(Species, -Number_of_records), 
                                      y = Number_of_records, fill = Species)) + 
  geom_bar(stat = "identity") + 
  theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.title = element_text(size = 14), 
    axis.text.x = element_text(size = 12, 
        vjust = 0.5, angle = 75), plot.title = element_text(size = 15), 
    panel.background = element_rect(fill = NA), 
    legend.background = element_rect(fill = NA, 
        size = 0.1)) +
  labs(x = "Species", size = 14) + 
  theme(legend.position = "none") + 
  coord_flip()  + 
  theme(axis.text.x = element_text(angle = 0))+ 
  geom_text(aes(label=Number_of_records), hjust=3, color="black", size=4) + 
  theme(axis.title = element_text(size = 16), 
    axis.text = element_text(size = 12), 
    plot.title = element_text(size = 14), 
    plot.background = element_rect(colour = NA)) +
  labs(y = "Number of records") + 
  theme(panel.grid.major = element_line(colour = NA), 
    panel.grid.minor = element_line(colour = NA), 
    panel.background = element_rect(linetype = "solid"), 
    plot.background = element_rect(linetype = "solid")) + 
  theme(axis.text = element_text(size = 14, 
    colour = "black"), axis.text.x = element_text(size = 14, 
    colour = "black"), axis.text.y = element_text(size = 14, 
    colour = "black"))

main_toxin_producers_cont + theme(
  panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA)
        )

ggsave("main_toxin_producers_cont.png", bg = "transparent")
  
  
```

```{r}
medcon %>% 
  filter(Continent == "Mediterranean") %>% 
  select(Species) %>% 
  group_by(Species) %>% 
  summarize(N = n()) %>% 
  arrange(desc(N))
```

```{r}
medcon6 <- medcon %>%
  filter(Continent == "Mediterranean") %>%
  select(Country, Cyanotoxin)%>%
  group_by(Country)%>%
  summarise(Number_of_records = n()) %>% 
  arrange(desc(Number_of_records))
medcon6
```

```{r}
med_country_cyanotox <- medcon %>% 
  filter(Continent == "Mediterranean")%>%
  select(Species, Country,Cyanotoxin)%>%
  group_by(Species, Cyanotoxin)%>%
  arrange(Cyanotoxin)
med_country_cyanotox

```


```{r}
number_continents <- medcon %>% 
  filter(Continent != "Mediterranean") %>% 
  select(Species, Continent,Cyanotoxin) %>% 
  group_by(Continent, Cyanotoxin) %>% 
  summarise(Toxin = n()) 
number_continents <- number_continents[-c(1,2), ]
number_continents

cont_stabar<- ggplot(number_continents, aes(x = Continent, y = Toxin, fill = Cyanotoxin)) + 
  geom_bar(stat = "identity")+
  geom_text(aes(label = Toxin), position = position_stack(vjust = 0.7)) + theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    panel.background = element_rect(fill = NA))

# transparent background
cont_stabar + theme(
  panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA)
        )

ggsave("cont_stabar.png", bg = "transparent")
```

## Different types of cyanotoxins found for the main toxin producers in Mediterranean

```{r}
cyanotoxins_per_species <- medcon %>% 
  filter(Continent == "Mediterranean") %>% 
  select(Species, Cyanotoxin) %>% 
  group_by(Species, Cyanotoxin) %>%
  summarize(Number_of_records = n()) %>% 
  arrange(desc(Number_of_records))
cyanotoxins_per_species


```

## Number of different types of cyanotoxins found in the world

```{r}
cyanotoxins_continents <- medcon %>%
  select(Cyanotoxin, Country) %>%
  group_by(Cyanotoxin) %>% 
  summarize(Number_of_records = n())
cyanotoxins_continent <- cyanotoxins_continents[-1, ]

number_cyanotoxins_cont <- ggplot(cyanotoxins_continent, 
                            aes(x=reorder(Cyanotoxin, - Number_of_records), 
                                Number_of_records, fill = Cyanotoxin)) + 
  geom_bar(stat="identity", position = "dodge") + 
  theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    panel.background = element_rect(fill = NA)) +
  labs(x = "Cyanotoxin", y = "Number of records") + 
  coord_flip() + theme(panel.grid.major = element_line(colour = NA), 
    axis.title = element_text(size = 16), 
    axis.text = element_text(size = 14), 
    legend.position = "none")

number_cyanotoxins_cont + theme(
  panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA)
        )

ggsave("number_cyanotoxins_cont.png", bg = "transparent", dpi = 300)
```

```{r}

```


