---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---



```{r import_data}
medcon <- read.csv("MED_Conts_Toxins_teliko_2.csv")
medcon

# Erase from the data.frame rows that contain broad categories of toxins (eg Hepatotoxin)
medcon <- medcon[-c(192,271,273, 431,836), ]

# Remove the unused levels from the Cyanotoxin factor
medcon <- droplevels(medcon)
medcon

# Check the levels
levels(medcon$Cyanotoxin)

```

```{r load_basic_libraries}
library(tidyr)
library(dplyr)
library(stringr)
library(ggplot2)
```

```{r}
summary(medcon)
```

## Find the unique Species in the Mediterranean basin

```{r}
medcon %>% 
  filter(Continent == "Mediterranean") %>% 
  group_by(Species) %>% 
  distinct(Species)
```


## Table with grouped Species and Cyanotoxins for each taxon in Mediterranean

```{r}
species_cyanotox <- medcon %>%
  filter(Continent == "Mediterranean")%>%
  group_by(Species, Cyanotoxin) %>%
  summarize(Number_of_records = n()) %>%
  select(Species,  Cyanotoxin)
species_cyanotox
```

```{r}
species_cyanotox_cont <- medcon %>%
  filter(Continent != "Mediterranean")%>%
  group_by(Species, Cyanotoxin) %>%
  summarize(Number_of_records = n()) %>%
  select(Species, Cyanotoxin )
species_cyanotox_cont
```

##Οι κύριοι παραγωγοί τοξινών στη Μεσόγειο (συνολικά 9) + γράφημα

```{r}
main_toxin_producers_MED <- medcon %>%
  filter(Continent == "Mediterranean")%>%
  group_by( Cyanotoxin, Species)%>%
  summarize(Number_of_records = n())%>%
  arrange(desc(Number_of_records))
main_toxin_producers_MED

head(main_toxin_producers_MED, 9)


main_toxin_producers_MED_plot <- 
  ggplot(head(main_toxin_producers_MED,9), 
         aes(x = reorder(Species, -Number_of_records), 
             y = Number_of_records, fill = Cyanotoxin)) + 
  geom_bar(stat = "identity") + 
  theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.title = element_text(size = 14), 
    axis.text.x = element_text(size = 12, 
        vjust = 0.5, angle = 75), plot.title = element_text(size = 15), 
    panel.background = element_rect(fill = NA),
    # legend.background = element_rect(fill = NA, 
        # size = 0.1)
    ) +
  labs(x = "Species", size = 14, colour = "white") + 
  # theme(legend.position = "none") +
  coord_flip()  + 
  theme(axis.text.x = element_text(angle = 0))+ 
  theme(axis.title = element_text(size = 16), 
    axis.text = element_text(size = 12), 
    plot.title = element_text(size = 14), 
    plot.background = element_rect(colour = NA)) +
  labs(y = "Number of records") + 
  theme(panel.grid.major = element_line(colour = NA), 
    panel.grid.minor = element_line(colour = NA), 
    panel.background = element_rect(linetype = "solid"), 
    plot.background = element_rect(linetype = "solid")) +
  theme(axis.text.y = element_text(face = "italic")) +
  # produce consistent colors across plots
  scale_fill_manual(values = c("Anatoxin" = "#7fc97f", 
                               "Saxitoxin" = "#beaed4",
                               "Cylindrospermopsin" = "#fdc086",
                               "Microcystin" = "#ffff99"))
 

main_toxin_producers_MED_plot
  
# Produce the plot with white text for the poster
transparent_main_toxin_producers_MED_plot <- main_toxin_producers_MED_plot + 
  theme(axis.ticks = element_line(colour = "white"), 
    axis.text = element_text(size = 20, colour = "white"), 
    axis.text.x = element_text(size = 14, 
        colour = "white"), axis.text.y = element_text(size = 14, 
        colour = "white")) + theme(axis.line = element_line(colour = "white"), 
    axis.ticks = element_line(colour = "white"), 
    axis.title = element_text(colour = "white"), 
    plot.title = element_text(colour = "white")) + 
    theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA)
        )

# No need to save it. A new image featuring both plots will be produced below
# ggsave("main_toxin_producers_MED.pdf", bg = "transparent")
  
```

## Main toxin producers in the other Continents, not Mediterranean

```{r}
main_toxin_producers_globally <- medcon %>%
  filter(Continent != "Mediterranean") %>% 
  group_by(Cyanotoxin, Species)%>%
  summarize(Number_of_records = n())%>%
  arrange(desc(Number_of_records))
main_toxin_producers_globally

main_toxin_producers_cont_plot <- 
  ggplot(head(main_toxin_producers_globally,8), 
        aes(x = reorder(Species, -Number_of_records), 
        y = Number_of_records, fill = Cyanotoxin)) + 
  geom_bar(stat = "identity") + 
  theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.title = element_text(size = 14), 
    axis.text.x = element_text(size = 12, 
        vjust = 0.5, angle = 75), plot.title = element_text(size = 15), 
    panel.background = element_rect(fill = NA), 
    # legend.background = element_rect(fill = NA, 
    #     size = 0.1)
    ) +
  labs(x = "Species", size = 14) + 
  # theme(legend.position = "none") +
  coord_flip()  + 
  theme(axis.text.x = element_text(angle = 0)) + 
  theme(axis.title = element_text(size = 16), 
    axis.text = element_text(size = 12), 
    plot.title = element_text(size = 14), 
    plot.background = element_rect(colour = NA)) +
  labs(y = "Number of records", colour = "white") + 
  theme(panel.grid.major = element_line(colour = NA), 
    panel.grid.minor = element_line(colour = NA), 
    panel.background = element_rect(linetype = "solid"), 
    plot.background = element_rect(linetype = "solid")) +
  theme(axis.text.y = element_text(face = "italic")) +
  # produce consistent colors across plots
  scale_fill_manual(values = c("Anatoxin" = "#7fc97f", 
                               "Saxitoxin" = "#beaed4",
                               "Cylindrospermopsin" = "#fdc086",
                               "Microcystin" = "#ffff99"))

main_toxin_producers_cont_plot  # check the plot
  
# Produce the plot with white text for the poster
transparent_main_toxin_producers_cont_plot <- main_toxin_producers_cont_plot +
  theme(axis.ticks = element_line(colour = "white"), 
    axis.text = element_text(size = 20, colour = "white"), 
    axis.text.x = element_text(size = 14, 
        colour = "white"), axis.text.y = element_text(size = 14, 
        colour = "white")) + theme(axis.line = element_line(colour = "white"), 
    axis.ticks = element_line(colour = "white"), 
    axis.title = element_text(colour = "white"), 
    plot.title = element_text(colour = "white")) + 
    theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA)
        )

# No need to save it. A new image featuring both plots will be produced below
# ggsave("main_toxin_producers_cont.pdf", bg = "transparent")
```

## Produce a single image for the two previous plots

```{r combined, fig.width=10}
med_subset <- head(main_toxin_producers_globally,8)
med_subset$subset <- "Mediterranean"

cont_subset <- head(main_toxin_producers_MED,9)
cont_subset$subset <- "Other Continents"

med_vs_cont <- rbind(med_subset, cont_subset)

combined <- 
  ggplot(med_vs_cont, 
          aes(x = reorder(Species, -Number_of_records), 
          y = Number_of_records, fill = Cyanotoxin)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~subset) +
  theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.title = element_text(size = 14), 
    axis.text.x = element_text(size = 12, 
        vjust = 0.5, angle = 75), plot.title = element_text(size = 15), 
    panel.background = element_rect(fill = NA), 
    # legend.background = element_rect(fill = NA, 
    #     size = 0.1)
    ) +
  labs(x = "Species", size = 14) + 
  # theme(legend.position = "none") +
  theme(legend.position = "bottom", legend.direction = "horizontal") +
  coord_flip()  + 
  theme(axis.text.x = element_text(angle = 0)) + 
  theme(axis.title = element_text(size = 16), 
    axis.text = element_text(size = 12), 
    plot.title = element_text(size = 14), 
    plot.background = element_rect(colour = NA)) +
  labs(y = "Number of records", colour = "white") + 
  theme(panel.grid.major = element_line(colour = NA), 
    panel.grid.minor = element_line(colour = NA), 
    panel.background = element_rect(linetype = "solid"), 
    plot.background = element_rect(linetype = "solid")) +
  theme(axis.text.y = element_text(face = "italic")) +
  # produce consistent colors across plots
  scale_fill_manual(values = c("Anatoxin" = "#7fc97f", 
                               "Saxitoxin" = "#beaed4",
                               "Cylindrospermopsin" = "#fdc086",
                               "Microcystin" = "#ffff99"))

combined

# Produce the plot with white text for the poster
transparent_combined_plot <- combined +
  theme(axis.ticks = element_line(colour = "white"), 
    axis.text = element_text(size = 20, colour = "white"), 
    axis.text.x = element_text(size = 14, 
        colour = "white"), axis.text.y = element_text(size = 14, 
        colour = "white")) + theme(axis.line = element_line(colour = "white"), 
    axis.ticks = element_line(colour = "white"), 
    axis.title = element_text(colour = "white"), 
    plot.title = element_text(colour = "white")) + 
    theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA),
        legend.text = element_text(colour = "white"),
        strip.background = element_blank(),
        strip.text = element_text(color = "white")
        )
  
ggsave("med_vs_cont.pdf", bg = "transparent")
```


```{r combined_plot, fig.asp=0.4, fig.width=10}
# if (!requireNamespace("ggpubr"))
#     install.packages("ggpubr")
# library(ggpubr)
# 
# ggarrange(main_toxin_producers_MED_plot,
#           main_toxin_producers_cont_plot,
#           labels = c("A", "B"),
#           common.legend = TRUE,
#           legend = "bottom")
# 
# ggsave("test.pdf", bg = "transparent")

```


## Number of cyanotoxins per species

```{r}
cyanotoxin_per_species <- medcon %>%
  filter(Continent == "Mediterranean")%>%
  select(Species, Country, Cyanotoxin)%>%
  group_by(Species, Cyanotoxin)%>%
  summarize(N_toxin = n())%>%
  arrange(Species, Cyanotoxin)
cyanotoxin_per_species

```

## Cyanotoxins per Species in the World except Mediterranean

```{r}
cyanotoxin_per_species <- medcon %>%
  filter(Continent != "Mediterranean")%>%
  select(Species, Country, Cyanotoxin)%>%
  group_by(Species, Cyanotoxin)%>%
  summarize(N_toxin = n())%>%
  filter(N_toxin >1) %>% 
  arrange(Species, Cyanotoxin)
cyanotoxin_per_species
```


```{r}
medcon %>% 
  filter(Continent == "Mediterranean") %>% 
  select(Species) %>% 
  group_by(Species) %>% 
  summarize(N = n()) %>% 
  arrange(desc(N))
```


```{r}
med_country_cyanotox <- medcon %>% 
  filter(Continent == "Mediterranean")%>%
  select(Species, Country,Cyanotoxin)%>%
  group_by(Species, Cyanotoxin)%>%
  arrange(Cyanotoxin)
med_country_cyanotox

```


```{r}
number_continents <- medcon %>% 
  filter(Continent != "Mediterranean") %>% 
  select(Species, Continent,Cyanotoxin) %>% 
  group_by(Continent, Cyanotoxin) %>% 
  summarise(Toxin = n()) 
number_continents <- number_continents[-c(1,2), ]
number_continents

cont_stabar<- ggplot(number_continents, aes(x = Continent, y = Toxin, fill = Cyanotoxin)) + 
  geom_bar(stat = "identity")+
   theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    panel.background = element_rect(fill = NA))

# white text, transparent background
cont_stabar + theme(axis.ticks = element_line(colour = "white"), 
    axis.title = element_text(size = 16, 
        colour = "white"), axis.text = element_text(size = 14, 
        colour = "white"), axis.text.x = element_text(size = 14), 
    legend.text = element_text(size = 12, 
        colour = "white"), legend.title = element_text(size = 14, 
        colour = "white"),
    panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA)) +
  labs(y = "Cyanotoxin")

ggsave("cont_stabar.pdf", bg = "transparent")
```

```{r}
number_cyanoto_med <- medcon %>% 
  filter(Continent == "Mediterranean") %>% 
  select(Species, Country,Cyanotoxin) %>% 
  group_by(Country, Cyanotoxin) %>% 
  summarise(Toxin= n()) 
number_cyanoto_med <- number_cyanoto_med[-c(1,2), ]
number_cyanoto_med

x <- ggplot(number_cyanoto_med, aes(x=reorder(Country, - Toxin), Toxin, fill=Cyanotoxin )) + geom_bar(stat = "identity")
x + theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.ticks = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = NA), 
    axis.title = element_text(size = 16, 
        colour = "white"), axis.text = element_text(size = 14, 
        colour = "white"), legend.text = element_text(size = 14, 
        colour = "white"), legend.title = element_text(size = 16, 
        colour = "white"), panel.background = element_rect(fill = NA), 
    plot.background = element_rect(colour = NA), 
    legend.key = element_rect(fill = NA), 
    legend.background = element_rect(fill = NA)) +labs(x = "Country", y = "Cyanotoxin")
x + theme(
  panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA))

ggsave("number_cyanoto_med.pdf", bg = "transparent")
```

## Different types of cyanotoxins found for the main toxin producers in Mediterranean

```{r}
cyanotoxins_per_species <- medcon %>% 
  filter(Continent == "Mediterranean") %>% 
  select(Species, Cyanotoxin) %>% 
  group_by(Species, Cyanotoxin) %>%
  summarize(Number_of_records = n()) %>% 
  arrange(desc(Number_of_records))
cyanotoxins_per_species


```

## Number of different types of cyanotoxins found in the world

```{r}
cyanotoxins_continents <- medcon %>%
  select(Cyanotoxin, Country) %>%
  group_by(Cyanotoxin) %>% 
  summarize(Number_of_records = n())
cyanotoxins_continent <- cyanotoxins_continents[-1, ]

number_cyanotoxins_cont <- ggplot(cyanotoxins_continent, 
                            aes(x=reorder(Cyanotoxin, - Number_of_records), 
                                Number_of_records, fill = Cyanotoxin)) + 
  geom_bar(stat="identity", position = "dodge") + 
  theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    panel.background = element_rect(fill = NA)) +
  labs(x = "Cyanotoxin", y = "Number of records") + 
  coord_flip() + theme(panel.grid.major = element_line(colour = NA), 
    axis.title = element_text(size = 16), 
    axis.text = element_text(size = 14), 
    legend.position = "none")

number_cyanotoxins_cont + theme(
  panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA),
        legend.background = element_rect(fill = NA)
        )

number_cyanotoxins_cont

# ggsave("number_cyanotoxins_cont.pdf", bg = "transparent", dpi = 300)
```



